---
title: "ghostie"
author: "m quigg"
date: "2026-06-22"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Ghost Orchid Pop Gen
This markdown is to analyze the population genetics of the ghost orchid for the University of Florida study. I used plink to generate the PCA while retaining individuals that have <50% missing data.

## Prep

### Libraries
```{r, include=FALSE}
#libraries
library(adegenet)
library(vcfR)
library(tidyverse)
library(pinfsc50)
library(dplyr)
library(poppr)
library(pegas)
library(PopGenReport)
library(hierfstat)
library(paletteer)
library(patchwork)
library(mapmixture)
library(gridExtra)
library(geodist)
library(vegan)
library(tinytex)
library(algatr)
library(maps)
library(tess3r)
library(rworldmap)
library(wingen)
library(terra)
library(raster)
library(viridis)
library(sf)
library(reshape2)
```

###Set Up
```{r}
#set working directory
setwd("C:/Users/mquig/Desktop/ghost_orchid")

#create custom color palette
custom_colors_ghost=c("#C969A1FF", "#EB7926FF", "#859B6CFF","#004F63FF", "#592688")
```

### Import metadata
```{r}
###import
meta=read.csv("input_data/metadata.csv", header = TRUE)

###clean
meta_clean <- meta %>% 
  dplyr::select(-c(X, X.1, X.2)) %>% 
  rename(Sample_ID = Sample..) %>% 
  separate(Sample_ID, into = c("Remove", "ind"), sep = "#") %>% 
  dplyr::select(-Remove) %>% 
  mutate(
    Group = case_when(
      Site == "1" ~ "1",
      Site %in% c("2", "5", "6", "7", "8", "9") ~ "2",
      Site %in% c("10", "11") ~ "3",
      Site == "3" ~ "4",
      Site == "4" ~ "5"))
```

## PCA
I want to start by making a PCA to see if we see clustering at all.
```{r}
###import the data###
strict_pca=read_table("input_data/ghostie.eigenvec", col_names = FALSE)
strict_eigenval=scan("input_data/ghostie.eigenval")

###clean up the data###
##remove extra ind column
strict_pca=strict_pca[,-1]

##rename the columnns##
names(strict_pca)[1]="ind"
names(strict_pca)[2:ncol(strict_pca)]=paste0("PC", 1:(ncol(strict_pca)-1))

###calculate percetage variance explained (PVE)###
##calculate it##
strict_pve=data.frame(PC=1:20, pve=strict_eigenval/sum(strict_eigenval)*100)

##graph it##
ggplot(strict_pve, aes(PC, pve)) +geom_bar(stat = "identity") +
  ylab("Percentage variance explained") +
  theme_classic()
#wow ok thats fairly low
#the highest PVE is ~13, not bad

##calculate the cumulative sum of the pve##
cumsum(strict_pve$pve)
#so PV 1,2,3 only account for 26% of the data


###graph the PCA###
strict_pca_plot=ggplot(strict_pca, aes(PC1, PC2))+
  geom_point(size = 2) + 
  #coord_equal() + 
  theme_classic() + 
  #geom_text(aes(label = ind), color = "black", nudge_x = 0.5, nudge_y = 0.5, size = 3) +
  xlab(paste0("PC1 (", signif(strict_pve$pve[1], 3), "%)")) + ylab(paste0("PC2 (", signif(strict_pve$pve[2], 3), "%)")) 
  #+ labs(title = "SNPs with 'strict' VCF filtering")
strict_pca_plot
```

### Incorporate Sites
```{r}
###clean up the PCA ind names
strict_pca=strict_pca %>% 
  separate(ind, into = c("ind", "delete"), sep = "_") %>% 
  dplyr::select(-delete)

###add metadata
strict_pca_meta=left_join(strict_pca, meta_clean, by = "ind")

###graph it
###graph the PCA###
sites_pca_plot=ggplot(strict_pca_meta, aes(PC1, PC2, color = as.factor(Group))) +
  geom_point(size = 3) + 
  #coord_equal() + 
  theme_classic() + 
  #geom_text(aes(label = ind), color = "black", nudge_x = 0.5, nudge_y = 0.5, size = 3) +
  xlab(paste0("PC1 (", signif(strict_pve$pve[1], 3), "%)")) + ylab(paste0("PC2 (", signif(strict_pve$pve[2], 3), "%)")) +
    scale_color_manual(values = c("#CE4441FF", "#EE8577FF", "#FFBB44FF", "#62929AFF", "#23469c", "#C969A1FF", "#EB7926FF", "#859B6CFF", "cornflowerblue", "#004F63FF", "#592688", "black", "cornflowerblue", "#9467bd"))+
  labs(color = "Group")

sites_pca_plot
```
## ADMIXTURE
```{r}
###import data###
CV_strict=read_table("input_data/combined.cv.error", col_names = FALSE)


###we have 10 replicates for each K value, so average them all###
CV_strict_summary=CV_strict %>% 
  group_by(X1) %>% 
  summarize(n=length(X1),
            mean=mean(X2),
            sd=sd(X2),
            se=sd/sqrt(n),
            lower.CI=mean-(1.96*se),
            upper.CI=mean+(1.96*se)) %>% 
  rename(K="X1")

###plot all of the CV scores
strict_allCV_plot=ggplot(CV_strict, aes(X1, X2)) +
  geom_point() +
  geom_smooth(color = "forestgreen", fill = "forestgreen", linewidth = 0.5, method = "loess", alpha = 0.3) +
  theme_classic() +
  ggtitle("All Cross-Validation Scores from ADMIXTURE (K= 1-15)") +
  labs(x ="Number of Populations (K)", y="Cross-Validation Score")
strict_allCV_plot

###plot the mean cross validation scores###
strict_CV_plot=ggplot(CV_strict_summary, aes(K, mean)) +
  geom_point() +
  #geom_smooth() +
  theme_classic() +
  ggtitle("Mean Cross-Validation Scores from ADMIXTURE (K= 1-15)")
strict_CV_plot
```
### Admixture plots by site
### K=10
For this we have 10 Sites that have sites in so we need the admixture results from K=10.
```{r}
###import the qmatrix data###
qmatrix=read.table("input_data/final_ghost_strict_LDpruned.10.1.Q")
nrow(qmatrix)
##add the sample IDs
qmatrix_samples=read.table("input_data/final_ghost_strict_LDpruned.fam")$V2
rownames(qmatrix)=qmatrix_samples
admixture_df=cbind(Sample_ID=rownames(qmatrix), qmatrix)

##fix the admixture df
admixture_df=admixture_df %>% 
  separate(Sample_ID, into = c("ind", "del"), sep = "_") %>% 
  dplyr::select(-del)
  

###merge the dataframes###
admixture_df=merge(admixture_df, meta_clean, by = "ind")

###clean it up###
##rename columns
admixture_df <- admixture_df %>%
  dplyr::rename(
    SampleID  = ind,
    Cluster1  = V1,
    Cluster2  = V2,
    Cluster3  = V3,
    Cluster4  = V4,
    Cluster5  = V5,
    Cluster6  = V6,
    Cluster7  = V7,
    Cluster8  = V8,
    Cluster9  = V9,
    Cluster10 = V10,
    #Cluster11= V11, 
    Site = Site)
##remove any ind not in a Site
admixture_df=admixture_df %>% filter(!is.na(Site) & Site != "")


###assign colors for the map###
cluster_colors=c("#CE4441FF", "#EE8577FF", "#FFBB44FF", "#62929AFF", "#23469c", "#859b6c", "cornflowerblue", "#004F63FF", "#592688", "#EB7926FF", "#e5b58e",  "#c969a1", "#592688", "#8164a5", "#004F63FF", "#8b9fa9", "#bac4ab")

```
Now I that the prep is done, I want to make the structure plot for the 12 Sites and combine them into one big figure.
```{r}
###graph it###
##reshape the data to long format
admix_long=admixture_df %>%
  pivot_longer(
    cols = starts_with("Cluster"),
    names_to = "Cluster",
    values_to = "Proportion")
##determine dominant cluster
dominant_df=admix_long %>%
  group_by(SampleID, Site) %>%
  slice_max(order_by = Proportion, n = 1, with_ties = FALSE) %>%
  dplyr::select(SampleID, Site, DominantCluster = Cluster, DominantProportion = Proportion)
##merge the two dataframes
admix_long=admix_long %>%
  left_join(dominant_df, by = c("SampleID", "Site"))
##reorder based on dominant cluster
admix_long=admix_long %>%
  mutate(SampleID = fct_reorder(SampleID, DominantProportion, .desc = TRUE))
##time to graph it!
ggplot(admix_long, aes(x = SampleID, y = Proportion, fill = Cluster)) +
  geom_bar(stat = "identity", width = 0.9) +
  facet_wrap(~ Site, ncol = 2, nrow = 6, scales = "free_x") +
  scale_fill_manual(values = cluster_colors) +
  theme_minimal() +
  theme(
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    panel.spacing = unit(0.2, "lines"),
    strip.text = element_text(size = 10),
    legend.position = "right"
  ) +
  labs(y = "Proportion", color = "Cluster")
```
### K=2
For this we have 10 Sites that have sites in so we need the admixture results from K=10.
```{r}
###import the qmatrix data###
qmatrix=read.table("input_data/final_ghost_strict_LDpruned.2.1.Q")
nrow(qmatrix)
##add the sample IDs
qmatrix_samples=read.table("input_data/final_ghost_strict_LDpruned.fam")$V2
rownames(qmatrix)=qmatrix_samples
admixture_df=cbind(Sample_ID=rownames(qmatrix), qmatrix)

##fix the admixture df
admixture_df=admixture_df %>% 
  separate(Sample_ID, into = c("ind", "del"), sep = "_") %>% 
  dplyr::select(-del)
  

###merge the dataframes###
admixture_df=merge(admixture_df, meta_clean, by = "ind")

###clean it up###
##rename columns
admixture_df <- admixture_df %>%
  dplyr::rename(
    SampleID  = ind,
    Cluster1  = V1,
    Cluster2  = V2,
    Site = Site)
##remove any ind not in a Site
admixture_df=admixture_df %>% filter(!is.na(Site) & Site != "")


###assign colors for the map###
cluster_colors2=c("#23469c", "#859b6c", "cornflowerblue", "#004F63FF", "#592688", "#EB7926FF", "#e5b58e",  "#c969a1", "#592688", "#8164a5", "#004F63FF", "#8b9fa9", "#bac4ab")

```
Now I that the prep is done, I want to make the structure plot for the 12 Sites and combine them into one big figure.
```{r}
###graph it###
##reshape the data to long format
admix_long=admixture_df %>%
  pivot_longer(
    cols = starts_with("Cluster"),
    names_to = "Cluster",
    values_to = "Proportion")
##determine dominant cluster
dominant_df=admix_long %>%
  group_by(SampleID, Site) %>%
  slice_max(order_by = Proportion, n = 1, with_ties = FALSE) %>%
  dplyr::select(SampleID, Site, DominantCluster = Cluster, DominantProportion = Proportion)
##merge the two dataframes
admix_long=admix_long %>%
  left_join(dominant_df, by = c("SampleID", "Site"))
##reorder based on dominant cluster
admix_long=admix_long %>%
  mutate(SampleID = fct_reorder(SampleID, DominantProportion, .desc = TRUE))
##time to graph it!
ggplot(admix_long, aes(x = SampleID, y = Proportion, fill = Cluster)) +
  geom_bar(stat = "identity", width = 0.9) +
  facet_wrap(~ Site, ncol = 2, nrow = 6, scales = "free_x") +
  scale_fill_manual(values = cluster_colors2) +
  theme_minimal() +
  theme(
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    panel.spacing = unit(0.2, "lines"),
    strip.text = element_text(size = 10),
    legend.position = "right") +
  labs(y = "Proportion", color = "Cluster")
```
### K=5
For this we have 5 groups so we need the admixture results from K=5.
```{r}
###import the qmatrix data###
qmatrix=read.table("input_data/final_ghost_strict_LDpruned.5.1.Q")
nrow(qmatrix)
##add the sample IDs
qmatrix_samples=read.table("input_data/final_ghost_strict_LDpruned.fam")$V2
rownames(qmatrix)=qmatrix_samples
admixture_df=cbind(Sample_ID=rownames(qmatrix), qmatrix)

##fix the admixture df
admixture_df=admixture_df %>% 
  separate(Sample_ID, into = c("ind", "del"), sep = "_") %>% 
  dplyr::select(-del)
  

###merge the dataframes###
admixture_df=merge(admixture_df, meta_clean, by = "ind")

###clean it up###
##rename columns
admixture_df <- admixture_df %>%
  dplyr::rename(
    SampleID  = ind,
    Cluster1  = V1,
    Cluster2  = V2,
    Cluster3 = V3,
    Cluster4 = V4,
    Cluster5 = V5,
    Site = Site)
##remove any ind not in a Site
admixture_df=admixture_df %>% filter(!is.na(Group) & Group != "")


###assign colors for the map###
cluster_colors2=c("#c969a1", "#bac4ab", "cornflowerblue", "#004F63FF", "#592688", "#EB7926FF", "#e5b58e",  "#c969a1", "#592688", "#8164a5", "#004F63FF", "#8b9fa9")

```
Now I that the prep is done, I want to make the structure plot for the 12 Sites and combine them into one big figure.
```{r}
###graph it###
##reshape the data to long format
admix_long=admixture_df %>%
  pivot_longer(
    cols = starts_with("Cluster"),
    names_to = "Cluster",
    values_to = "Proportion")
##determine dominant cluster
dominant_df=admix_long %>%
  group_by(SampleID, Group) %>%
  slice_max(order_by = Proportion, n = 1, with_ties = FALSE) %>%
  dplyr::select(SampleID, Group, DominantCluster = Cluster, DominantProportion = Proportion)
##merge the two dataframes
admix_long=admix_long %>%
  left_join(dominant_df, by = c("SampleID", "Group"))
##reorder based on dominant cluster
admix_long=admix_long %>%
  mutate(SampleID = fct_reorder(SampleID, DominantProportion, .desc = TRUE))
##time to graph it!
ggplot(admix_long, aes(x = SampleID, y = Proportion, fill = Cluster)) +
  geom_bar(stat = "identity", width = 0.9) +
  facet_wrap(~ Group, ncol = 2, nrow = 6, scales = "free_x") +
  scale_fill_manual(values = custom_colors_ghost) +
  theme_minimal() +
  theme(
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    panel.spacing = unit(0.2, "lines"),
    strip.text = element_text(size = 10),
    legend.position = "right") +
  labs(y = "Proportion", color = "Cluster")
```

## Genetic Diversity
Tutorials used: https://popgen.nescent.org/StartSNP.html, https://medium.com/@tarangds/knn-imputation-the-complete-guide-146f932870a7

### Import Data
This is made using a vcf file with only biallelic sites and LD pruning! It is a different input file from the PCA. There are 72 individuals.
```{r, include=FALSE}
###import data###
##for this I need a genind object
strict_vcf_ld=read.vcfR("input_data/final_ghost_strict_LDpruned.vcf", verbose = FALSE)

###convert to genind
strict_genind=vcfR2genind(strict_vcf_ld)
```

### Impute Missing Data
From here on out, these programs cannot handle missing data. So, I need to find a way to impute the missing genotypes. For this, I want to do a nearest neighbor approach. What this does, is take the most genetically similar individuals and impute the most common genotype (alternatively you can use the mean but most of these programs can only handle discreet genotypes).
```{r}
###convert the genotypes
##convert genind to dataframe
ghost_df=genind2df(strict_genind)
##fix rownames
rownames(ghost_df) <- gsub("^(.*)_\\1$", "\\1", rownames(ghost_df))
##convert alleles to numeric genotypes
ghost_geno=apply(ghost_df, 2, function(x) {
  x[x == "00"] <- 0  # A/A
  x[x == "01"] <- 1  # A/B
  x[x == "10"] <- 1  # B/A
  x[x == "11"] <- 2  # B/B
  as.numeric(x)
})
##make sure its all numeric
ghost_geno=as.data.frame(ghost_geno)
##convert rownames
rownames(ghost_geno) <- rownames(ghost_df)

###calculate genetic similarity
library(proxy)

##compute pairwise distances (ignoring NAs)
ghost_geno_dist=dist(ghost_geno, method = "euclidean")
ghost_geno_dist_matrix=as.matrix(ghost_geno_dist)

###impute using k nearest neighbor
##make a function for mode
get_mode <- function(v) {
  v <- v[!is.na(v)]
  if (length(v) == 0) return(NA)
  uniqv <- unique(v)
  uniqv[which.max(tabulate(match(v, uniqv)))]
}
##make the function
impute_knn <- function(genotype_matrix, dist_matrix, k = 5) {
  imputed <- genotype_matrix
  for (i in 1:nrow(genotype_matrix)) {
    missing_loci <- which(is.na(genotype_matrix[i, ]))
    if (length(missing_loci) > 0) {
      neighbors <- order(dist_matrix[i, ], decreasing = FALSE)[2:(k + 1)]
      for (locus in missing_loci) {
        neighbor_values <- genotype_matrix[neighbors, locus]
        mode_val <- get_mode(neighbor_values)
        if (!is.na(mode_val)) {
          imputed[i, locus] <- mode_val
        }
      }
    }
  }
  rownames(imputed) <- rownames(genotype_matrix)
  return(imputed)
}

##generate the output
ghost_impute=impute_knn(ghost_geno, ghost_geno_dist_matrix, k=5)
head(ghost_impute)

##double check
sum(is.na(ghost_impute))
#it worked!!!

###convert back to genind
##convert back to alleles
geno_char=as.data.frame(lapply(ghost_impute, function(x) {
  x <- as.character(x)
  x[x == "0"] <- "00"
  x[x == "1"] <- "01"
  x[x == "2"] <- "11"
  return(x)
}))
rownames(geno_char)=rownames(ghost_impute)

##convert to genind
colnames(geno_char) <- paste0("Locus", seq_len(ncol(geno_char)))

ghost_impute_genind=df2genind(geno_char, sep = "", ncode = 2, ploidy = 2, ind.names = rownames(geno_char))
```
### Assess Genetic Diversity
```{r}
###overall
ghost_stats=basic.stats(ghost_impute, diploid = TRUE, digits = 4)
ghost_stats$overall

###allelic richness
adegenet::summary(strict_genind)
```

#### Genetic Diversity per group
```{r}
###add the pops
ghost_impute_groups=rownames_to_column(ghost_impute, var = "ind")
ghost_impute_groups=ghost_impute_groups %>% 
  separate(ind, into = c("ind", "delete"), sep = "_") %>% dplyr::select(-delete)
ghost_impute_groups=right_join(meta_clean, ghost_impute_groups, by = "ind")
ghost_impute_groups=ghost_impute_groups %>% 
  dplyr::select(-c(E, N, Site, NAOCC.ID, Permit)) %>% 
  column_to_rownames(var = "ind") %>% 
  rename("pop"="Group")

###convert to genind
pop_vec <- ghost_impute_groups[,1]              # first column = population
geno_mat <- ghost_impute_groups[,-1]            # remaining columns = SNPs
rownames(geno_mat) <- rownames(ghost_impute_groups)
convert_numeric_to_alleles <- function(x, ref="A", alt="T") {
  ifelse(x == 0, paste(ref, ref, sep="/"),
  ifelse(x == 1, paste(ref, alt, sep="/"),
  ifelse(x == 2, paste(alt, alt, sep="/"), NA)))}
geno_char <- as.data.frame(apply(geno_mat, 2, convert_numeric_to_alleles))
genind_ghost_groups <- df2genind(
  geno_char,
  ploidy = 2,
  sep = "/",
  pop = pop_vec,
  NA.char = "NA")

###calculate diversity
poppr(genind_ghost_groups)
summary(genind_ghost_groups)

ghost_impute_groups$pop <- as.factor(ghost_impute_groups[,1])
ghost_impute_groups <- ghost_impute_groups[!is.na(ghost_impute_groups[,1]), ]
div_groups=basic.stats(ghost_impute_groups)
Ho_pop  <- colMeans(div_groups$Ho, na.rm = TRUE)
He_pop  <- colMeans(div_groups$Hs, na.rm = TRUE)
Fis_pop <- colMeans(div_groups$Fis, na.rm = TRUE)
div_table <- data.frame(
  Population = names(Ho_pop),
  Ho = Ho_pop,
  He = He_pop,
  Fis = Fis_pop
)

div_table

```

#### Genetic Diversity per Site
```{r}
###add the pops
ghost_impute_site=rownames_to_column(ghost_impute, var = "ind")
ghost_impute_site=ghost_impute_site %>% 
  separate(ind, into = c("ind", "delete"), sep = "_") %>% dplyr::select(-delete)
ghost_impute_site=right_join(meta_clean, ghost_impute_site, by = "ind")
ghost_impute_site=ghost_impute_site %>% 
  dplyr::select(-c(E, N, Group, NAOCC.ID, Permit)) %>% 
  column_to_rownames(var = "ind") %>% 
  mutate(Site_label="site") %>% 
  unite(col = "site", Site_label, Site, sep = "") %>%
  rename("pop"="site")

###convert to genind
pop_vec <- ghost_impute_site[,1]              # first column = population
geno_mat <- ghost_impute_site[,-1]            # remaining columns = SNPs
rownames(geno_mat) <- rownames(ghost_impute_site)
convert_numeric_to_alleles <- function(x, ref="A", alt="T") {
  ifelse(x == 0, paste(ref, ref, sep="/"),
  ifelse(x == 1, paste(ref, alt, sep="/"),
  ifelse(x == 2, paste(alt, alt, sep="/"), NA)))}
geno_char <- as.data.frame(apply(geno_mat, 2, convert_numeric_to_alleles))
genind_ghost_site <- df2genind(
  geno_char,
  ploidy = 2,
  sep = "/",
  pop = pop_vec,
  NA.char = "NA")

###calculate diversity
poppr(genind_ghost_site)
summary(genind_ghost_site)

ghost_impute_site$pop <- as.factor(ghost_impute_site[,1])
ghost_impute_site <- ghost_impute_site[!is.na(ghost_impute_site[,1]), ]
div_groups=basic.stats(ghost_impute_site)
Ho_pop  <- colMeans(div_groups$Ho, na.rm = TRUE)
He_pop  <- colMeans(div_groups$Hs, na.rm = TRUE)
Fis_pop <- colMeans(div_groups$Fis, na.rm = TRUE)
div_table <- data.frame(
  Population = names(Ho_pop),
  Ho = Ho_pop,
  He = He_pop,
  Fis = Fis_pop
)

div_table

```

##### Fst Heatmap per site
This uses the package heirfstat and is based on the Weir & Cockerham estimator of Fst.
```{r}
###extract the pops with only 1 individual
pop_sizes <- table(pop(genind_ghost_site))
small_pops <- names(pop_sizes[pop_sizes < 2])

###remove the pops with only 1 individual
genind_ghost_sites_filtered=popsub(genind_ghost_site, exclude = small_pops)

###calculate Fst
Fst_hierfstat=hierfstat::pairwise.WCfst(genind_ghost_sites_filtered, diploid = TRUE)

###covert to matrix
Fst_matrix=as.matrix(Fst_hierfstat)

###order the populations
pop_levels <- c("site1", "site2", "site3", "site5", "site6", "site7", "site8", "site10", "site11")

###reorder the matrix
fst_matrix <- Fst_matrix[pop_levels, pop_levels]

###melt
fst_melt <- melt(Fst_matrix, na.rm = FALSE)

###change the negative values to 0s
fst_melt=fst_melt %>% 
  mutate(value = replace_na(value, 0)) %>% 
  rename("Fst"=value)
fst_melt$Fst[fst_melt$Fst<0]="0"
fst_melt$Fst=as.numeric(fst_melt$Fst)
fst_melt$Var1=as.character(fst_melt$Var1)
fst_melt$Var2=as.character(fst_melt$Var2)


fst_melt$Var1 <- factor(fst_melt$Var1, levels = pop_levels)
fst_melt$Var2 <- factor(fst_melt$Var2, levels = pop_levels)

# Keep only upper triangle (including diagonal)
fst_melt <- fst_melt %>%
  filter(as.integer(Var1) <= as.integer(Var2))

###graph it
ggplot(fst_melt, aes(x = Var1, y = Var2, fill = Fst)) +
  geom_tile(color = "white") +
  geom_text(aes(label = round(Fst, 3)), color = "black", size = 3) +
  scale_x_discrete(limits = pop_levels, position = "top") +
  scale_y_discrete(limits = pop_levels) +
  scale_fill_gradientn(
    colors = RColorBrewer::brewer.pal(9, "Greens"),
    limits = c(0, 1),
    name   = "Fst"
  ) +
  theme_minimal() +
  theme(
    axis.text.x  = element_text(angle = 45, hjust = 1),
    axis.title   = element_blank(),
    panel.grid   = element_blank()
  ) +
  ggtitle("Pairwise Weir-Cockerham Fst")
```
